---
title: "Untitled"
author: "Sarah Hvid Andersen"
date: "15/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
pacman::p_load(tidyverse, igraph, visNetwork, networkD3, data.table)
```

```{r}
links <- read_csv('data_links.csv')

links <- links %>% filter(source != 'x') %>% filter(target != 'x')
```

```{r}
nodes <- unique(links$source) %>% as.data.frame()
nodes <- nodes %>% rowid_to_column("id") %>% rename('label' = '.')
```


```{r}
per_route <- links %>%  
  group_by(source, target) %>%
  summarise(weight = n()) %>% 
  ungroup()


#per_route <- per_route %>% filter(weight >= 2)
```


```{r}
edges <- per_route %>% 
  left_join(nodes, by = c("source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("target" = "label")) %>% 
  rename(to = id)

#edges <- select(edges, from, to, weight)

```

```{r}
g3 <- igraph::graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)
g3 <- simplify(g3)
g3
```


from: https://www.r-bloggers.com/2018/12/network-centrality-in-r-an-introduction/ 

```{r}
cent <- tibble(nodes=1:vcount(g3))
cent$id <- nodes$label


cent$degree <- igraph::degree(g3)
cent$betweenness <- igraph::betweenness(g3)
cent$closeness <- igraph::closeness(g3)
cent$eigen <- igraph::eigen_centrality(g3)$vector
cent$subgraph <- igraph::subgraph_centrality(g3)
```

centrality:
In a nutshell, a measure of centrality is an index that assigns a numeric values to the nodes of the network. The higher the value, the more central the node (A more thorough introduction is given in the extended tutorial).

degree:
The degree of a vertex is its most basic structural property, the number of its adjacent edges.

betweenness:
The vertex and edge betweenness are (roughly) defined by the number of geodesics (shortest paths) going through a vertex or an edge.

closeness:
Closeness centrality measures how many steps is required to access every other vertex from a given vertex.

link: https://kateto.net/network-visualization 

```{r}

bar_plot <- function(dataframe, x_var, y_var, sub_title) {
  cent_s <- dataframe %>%
    slice_max({{y_var}}, n = 15) %>% 
    arrange(desc({{y_var}}))
  
  ggplot(cent_s, aes(x = {{x_var}}, y = {{y_var}}, color = {{x_var}}))+
    geom_bar(stat = 'identity', fill = 'grey') + 
    scale_x_discrete(limits = cent_s$id) +
    theme(legend.position = 'none') +
    ggtitle('Network Analysis', subtitle = sub_title)
  
}

bar_plot(cent, id, degree, 'degree')
bar_plot(cent, id, betweenness, 'betweenness')
bar_plot(cent, id, closeness, 'closeness')
bar_plot(cent, id, eigen, 'eigen')
bar_plot(cent, id, subgraph, 'subgraph')
```


```{r}
routes_tidy <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
```


```{r}
nodes_d3 <- mutate(nodes, id = id - 1)

dt <- data.table(edges)
dt2 <- dt[,list(sum_weight = sum(weight), freq = .N), by = c('source')]

nodes$sum_weight <- dt2$sum_weight

edges_d3 <- mutate(edges, from = from - 1, to = to - 1)
```


```{r}
forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", Nodesize = 'sum_weight', 
             opacity = 1, fontSize = 18, zoom = TRUE)
```


