---
title: "Script 4"
author: "Sarah Hvid Andersen"
date: "07/01/2022"
output: html_document
---

This script creates two networks. One for analysis, and one for visualization. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading packages:

```{r}
pacman::p_load(tidyverse, igraph, visNetwork, networkD3, data.table)
```

We then load the 'data_links.csv' file after the preprocessing in OpenRefine has been applid. 
Change the working directory to the csv folder within the strings of the first line of code. 
Some of the gathered entities were not names and were altered to an 'x' in the dataframe. These should be removed.

```{r}
setwd("C:/Users/Sarah/Desktop/Bachelor/Ibsen/ibsen_network/data/csv")

links <- read_csv('OR_data_links.csv')

links <- links %>% filter(source != 'x') %>% filter(target != 'x')
```

Now, we can create a dataframe of the nodes by getting each unique name in the dataframe. 

```{r}
nodes <- unique(links$source) %>% as.data.frame()
nodes <- nodes %>% rowid_to_column("id") %>% rename('label' = '.')
```

Then, we can calculate the weights of the network.

```{r}
per_route <- links %>%  
  group_by(source, target) %>%
  summarise(weight = n()) %>% 
  ungroup()

```

And from the weights, we create the dataframe of the edges.

```{r}
edges <- per_route %>% 
  left_join(nodes, by = c("source" = "label")) %>% 
  rename(from = id)

edges <- edges %>% 
  left_join(nodes, by = c("target" = "label")) %>% 
  rename(to = id)

edges <- select(edges, from, to, weight)

```

Now we can create the first network using the Igraph package. 

```{r}
g3 <- igraph::graph_from_data_frame(d = edges, vertices = nodes, directed = FALSE)
g3 <- simplify(g3)
g3
```

From the network, we calculate different centrality measures. In a nutshell, a measure of centrality is an index that assigns a numeric values to the nodes of the network. The higher the value, the more central the node (A more thorough introduction is given in the extended tutorial).


```{r}
cent <- tibble(nodes=1:vcount(g3))
cent$id <- nodes$label


cent$degree <- igraph::degree(g3)
cent$betweenness <- igraph::betweenness(g3)
cent$closeness <- igraph::closeness(g3)
cent$eigen <- igraph::eigen_centrality(g3)$vector
cent$subgraph <- igraph::subgraph_centrality(g3)
```


degree:
The degree of a vertex is its most basic structural property, the number of its adjacent edges.

betweenness:
The vertex and edge betweenness are (roughly) defined by the number of geodesics (shortest paths) going through a vertex or an edge.

closeness:
Closeness centrality measures how many steps is required to access every other vertex from a given vertex.


Then we can write a function that creates a barplot illustrating the different measures. 

```{r}

bar_plot <- function(dataframe, x_var, y_var, sub_title) {
  cent_s <- dataframe %>%
    slice_max({{y_var}}, n = 15) %>% 
    arrange(desc({{y_var}}))
  
  ggplot(cent_s, aes(x = {{x_var}}, y = {{y_var}}, color = {{x_var}}))+
    geom_bar(stat = 'identity', fill = 'grey') + 
    scale_x_discrete(limits = cent_s$id) +
    theme(legend.position = 'none') +
    ggtitle('Network Analysis', subtitle = sub_title)
  
}

bar_plot(cent, id, degree, 'degree')
bar_plot(cent, id, betweenness, 'betweenness')
bar_plot(cent, id, closeness, 'closeness')
bar_plot(cent, id, eigen, 'eigen')
bar_plot(cent, id, subgraph, 'subgraph')
```

We also want to create a network for visualization purposes. The NetworkD3 package is useful for this, and it also allows interactivty. It requires a slightly different setup, starting from 0 instad of 1. 

```{r}
nodes_d3 <- mutate(nodes, id = id - 1)
edges_d3 <- mutate(edges, from = from - 1, to = to - 1)
```

With the setup done, we can now create the network. It includes interactive labels. Hovering over a node, will show the name of the node. You can also zoom in and out, focusing on different parts of the network.

```{r}
forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 18, zoom = TRUE)
```

References:

schochastics. (2018, December 7). Network Centrality in R: An Introduction | R-bloggers. https://www.r-bloggers.com/2018/12/network-centrality-in-r-an-introduction/

Ognyanova, K. (2021, June 26). Static and dynamic network visualization with R. Katya Ognyanova. https://kateto.net/network-visualization/